\Title

### 2020-02-18 manuscript/manuscript.tex
Make target grid figure on single column
Replace variable depth on table and fig caption

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
    \caption{
        Depth types for locating point sources. We put one source beneath each
        observation point (station) using: (a)~a \emph{constant depth} where
        all sources are located at the same depth, (b)~a \emph{relative depth}
        where all sources are located at the same vertical distance from its
        corresponding observation point, and (c)~a \emph{variable relative
        depth} where the depth of the sources is proportional to the average
        distance to its neighbour sources. Notice how the clustered sources on
        (c) are relatively shallower than the other ones.
    }
    \label{fig:depth-types}
\end{figure*}

@@

\begin{table*}
\begin{minipage}{80mm}
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source bellow data & Block averaged sources & Grid sources \\ \hline
        Constant depth          & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth          & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{minipage}
\end{table*}

@@

\begin{figure*}
    %\includegraphics[width=\linewidth]{}
    \caption{
        Target grid. Gravitational effect of synthetic model on a regular grid
        composed of 56$\times$57 points with a spacing of \SI{2}{\km} located
        \SI{2000}{\m} above the zero height plane.
    }
    \label{fig:target-grid}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
    \caption{
        Depth types for locating point sources. We put one source beneath each
        observation point (station) using: (a)~a \emph{constant depth} where
        all sources are located at the same depth, (b)~a \emph{relative depth}
        where all sources are located at the same vertical distance from its
        corresponding observation point, and (c)~a \emph{variable depth} where
        the depth of the sources is proportional to the average distance to its
        neighbour sources. Notice how the clustered sources on (c) are
        relatively shallower than the other ones.
    }
    \label{fig:depth-types}
\end{figure*}

@@

\begin{table*}
\begin{minipage}{80mm}
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source bellow data & Block averaged sources & Grid sources \\ \hline
        Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{minipage}
\end{table*}

@@

\begin{figure}
    %\includegraphics[width=\linewidth]{}
    \caption{
        Target grid. Gravitational effect of synthetic model on a regular grid
        composed of 56$\times$57 points with a spacing of \SI{2}{\km} located
        \SI{2000}{\m} above the zero height plane.
    }
    \label{fig:target-grid}
\end{figure}
